\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-03 doc/paper.tex
doc/paper.tex: fix a dangling ref
add Higgs triplet expression for theta_W, as suggested by Dominik

type-specific constants \cite{Hall:1980kf}

@@

@@

  .

@@

  \left(M_W^{\text{pole}}\right)^2 + \re \Pi_{WW}^T(p^2 = (M_W^{\text{pole}})^2, \mu=M_Z) ,\\

@@

  \left(M_Z^{\text{pole}}\right)^2 + \re \Pi_{ZZ}^T(p^2 = (M_Z^{\text{pole}})^2, \mu=M_Z) ,

@@

where $M_W^{\text{pole}} = 80.404\unit{GeV}$ and $M_Z^{\text{pole}} =
91.1876\unit{GeV}$ \cite{Beringer:1900zz}.  Having
$\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$ allows to calculate the
(GUT-normalized) $U(1)_Y$ and $SU(2)_L$ gauge couplings in the SUSY
model.  In the MSSM one has for instance

@@

As already emphasized in \secref{sec:design goals}, the modular design of
\fs makes it straightforward % to change a boundary condition.
% Within the present C++ code structure,
% this task reduces
to replace a boundary condition object.
The question then becomes how
one could obtain an alternative boundary condition class,
apart from writing one by hand.
The meta code feature of \fs offers great assistance
in this respect.
An example shall be presented to illustrate how this works.

>>>>

type specific constants \cite{Hall:1980kf}

@@

  \theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z) &= \arcsin\sqrt{1
    -
  ,
while in models with Higgs triplets the relation looks like

@@

    \frac{\left(M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2 -
      g_2^2v_T^2}{\left(M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2}}.

@@

  M_W^2 + \re \Pi_{WW}^T(p^2 = M_W^2, \mu=M_Z) ,\\

@@

  M_Z^2 + \re \Pi_{ZZ}^T(p^2 = M_Z^2, \mu=M_Z) ,

@@

where $M_W = 80.404\unit{GeV}$ and $M_Z = 91.1876\unit{GeV}$
\cite{Beringer:1900zz}.  Having $e_{\text{susy}}^{\text{\DRbar}}(M_Z)$
and $\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$ allows to calculate
the (GUT-normalized) $U(1)_Y$ and $SU(2)_L$ gauge couplings in the
SUSY model.  In the MSSM one has for instance

@@

As already emphasized in \secref{Sec:Program}, the modular design of
\fs makes it straightforward % to change a boundary condition.
% Within the present C++ code structure,
% this task reduces
to replace a boundary condition object.
The question then becomes how
one could obtain an alternative boundary condition class,
apart from writing one by hand.
The meta code feature of \fs offers great assistance
in this respect.
An example shall be presented to illustrate how this works.
